XOR-Some Prolific Pilot 1

### 2021-03-25 analysis/xor-some-prolific-pilot1.Rmd
start first Prolific pilot analysis

```{r}
d_critical <- d_critical %>% 
  pivot_longer(c(competence, relevance, prior), 
               names_to = "class_condition", 
               values_to = "prior_class")
d_critical %>% 
  filter(block != "xor" & block != "some") %>%
  ggplot(., aes(x = as.factor(prior_class), y = response)) +
  geom_point(size = 2, alpha = 0.3, position = position_jitter(width = 0.1)) +
    facet_wrap(main_type~class_condition)
```
Plot main rel / comp questions by main condition, separated into with / without critical utterance
```{r}
# add info to already record this
d_critical <- d_critical %>% 
  mutate(w_utterance = ifelse(is.na(critical_question), F, T))

d_critical %>% 
  filter(block != "xor" & block != "some") %>%
  ggplot(., aes(x = as.factor(prior_class), y = response, color = w_utterance)) +
  geom_point(size = 2, alpha = 0.3, position = position_jitter(width = 0.1)) +
    facet_wrap(main_type~class_condition) # get ratings from the respective trials only 
# use block for getting the actual correct ratings, but class_condition for subsetting the prior classification fo the respective predictor 
```

>>>>

```{r}
d_critical <- d_critical %>% 
  pivot_longer(c(competence, relevance, prior), 
               names_to = "class_condition", 
               values_to = "prior_class")
d_critical %>% 
  filter(block != "xor" & block != "some") %>%
  ggplot(., aes(x = as.factor(prior_class), y = response)) +
  geom_point(size = 2, alpha = 0.3, position = position_jitter(width = 0.1)) +
    facet_wrap(main_type~class_condition)
```
Plot main rel / comp questions by main condition, separated into with / without critical utterance
```{r}
# add info to already record this
d_critical <- d_critical %>% 
  mutate(w_utterance = ifelse(is.na(critical_question), F, T),
         block = ifelse(block == "comp", "competence", 
                        ifelse(block == "rel", "relevance", "prior")))

d_critical %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  ggplot(., aes(x = as.factor(prior_class), y = response, color = w_utterance)) +
  geom_point(size = 2, alpha = 0.3, position = position_jitter(width = 0.1)) +
    facet_wrap(main_type~class_condition) # get ratings from the respective trials only 
# use block for getting the actual correct ratings, but class_condition for subsetting the prior classification fo the respective predictor

# some condition was wrongly recorded as pri
d_critical %>% 
     filter(block != "xor" & block != "some") %>%
     filter(block == class_condition) %>% filter(block == "prior" & w_utterance == T) %>% View()

```
